Analysis

### 2020-01-16 script/analysis.Rmd
update

```{r}
load("input/data/processed/clw3.RData")
load("input/data/processed/dat99.RData")
load("input/data/processed/dat09.RData")
load("input/data/processed/dat19.RData")
names(clw3)

@@

```{r}
options(knitr.kable.NA = '')
kable(desc01,format = "html",
      align = c("l"),
      booktabs=T,
      row.names = F,
      col.names = c("Año","Dimensión","N","Variable/nivel","Media(DS)/%","Min","Max")) %>%
  kable_styling(full_width = F) %>%
  collapse_rows(columns = 1:2,valign = "middle",row_group_label_position = 'stack') %>%
  cat(., file = "output/tables/desc.html")

tab03$var <- rownames(tab03)
tab03$var[tab03$var=="lngap_perc"] <- "Percibida"
tab03$var[tab03$var=="lngap_just"] <- "Justa"

tab03$mod <- c("Brecha Salarial","Brecha Salarial","Educación","Educación","Educación","Educación",
               "Ingreso","Ingreso","Ingreso","Ingreso","Ingreso")

tab03 <- select(tab03,mod,var,everything())

sink("output/tables/desc.html")
kableExtra::kable(tab03,format = "html",booktabs=T ,row.names = F,col.names = c("Dimensión","N","Variable/niveles","Media(DS)","Min","Max")) %>%
  kable_styling() %>%
    collapse_rows(columns = 1,valign = "middle")
sink()
```

>>>>

```{r}
load("input/data/processed/clw3.Rdata")
load("input/data/processed/dat99.RData")
load("input/data/processed/dat09.RData")
load("input/data/processed/dat19.RData")
names(clw3)

@@

```{r}
options(knitr.kable.NA = '')
kable(desc01,format = "html",
      align = c("l"),
      booktabs=T,
      row.names = F,
      col.names = c("Año","Dimensión","N","Variable/nivel","Media(DS)/%","Min","Max")) %>%
  kable_styling(full_width = F) %>%
  collapse_rows(columns = 1:2,valign = "middle",row_group_label_position = 'stack')

%>%
  cat(., file = "output/tables/desc.html") # finalmente guardado como html desde el viewer para que aparezcan las líneas
